How crisis affect the low-income and high-income economies differently

### 2024-04-09 paper/paper.qmd
Working on Models

```{r}

@@

```{r}
highmodel <- glm(gni_per_cap ~ gdp_growth + population + unem_rate + lf_par_rate + trade_per + inflation, 
             family = gaussian(link = "identity"), data = highincome)

>>>>

```{r}
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| echo: false
#| warning: false
#| message: false
highmodel <- glm(gni_per_cap ~ gdp_growth + population + unem_rate + lf_par_rate + trade_per + inflation, 
             family = gaussian(link = "identity"), data = highincome)
